---
title: "Programming Background"
author: "Evan Patton"
date: "9/11/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, message = FALSE, warning = FALSE, fig.path = "../images/")
```

## Programming Experience Before ST 558

Before starting this course my programming experience was:  

*  **SAS**    - [Certified](https://www.certmetrics.com/SAS/public/candidate_directory_search.aspx) in Base Programming 9.4
*  **R**      - Have been teaching myself and using [Datacamp](https://www.datacamp.com/) for about 1.5 years.
*  **SQL**    - Limited experience, but a general understanding.
*  **Python** - Very limited experience.

Personally R is my favorite program and language that I have used so far. I think R tends to be more user friendly and there is often a lot of way to do the same thing and each programmer can use their favorite way. Other programs tend to be more specific about the way to do things. I will say that SAS does an excellent job of making reports that are ready for presentation to stakeholders. SAS also being non open source always has someone or a resource that you can ask for help with a problem whereas with R because its open source there's no person or organization to turn to for solid answers.

Overall I don't think R is too hard to learn. Once you know the basics it is not that hard to go to the next level.

At first I was definitely overwhelmed but after understanding definitions of things and how extremely useful packages were (especially the tidyverse), I feel as if I have been able to learn R pretty well.


## R Markdown output

```{r plot}
plot(iris)
```


